\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}


\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}
% \usepackage{emoji}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% ----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Tianyu Hua} \\ \vspace{1pt}
    \small 604-790-8826 $|$ \href{mailto:patrickhua.ty@gmail.com}{\underline{patrickhua.ty@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/tianyu-hua-876865180/}{\underline{linkedin.com}} $|$
    \href{http://patrickhua.github.io/}{\underline{patrickhua.github.io}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of British Columbia \& Vector Institute; Advisor: Prof. Leonid Sigal}{BC, Canada}
      % {, Supervisor: Prof. Leonid Sigal}
      {Master of Science in Computer Science (M.Sc.)}{Expected in Jun. 2023}
      % test
    \resumeSubheading
      {Queen’s University}{Ontario, Canada}
      {Exchange Student}{Jan. 2019 -- May 2019}
    \resumeSubheading
      {China University of Geosciences}{Beijing, China}
      {Bachelor of Computer Science, GPA: 89.19/100 (TOP 5\%)}{Sep. 2016 -- Jun. 2020}

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Research Assistant; Advisor: Prof. Leonid Sigal}{From Sep. 2021}
    {Vector Insititute}{Toronto, Canada}
    \resumeItemListStart
      \resumeItem{\href{https://arxiv.org/pdf/2203.12054.pdf}{\color{blue}{\textbf{\underline{Paper}}}} \textbf{\textit{Self-supervision through Random Segments with Autoregressive Coding (RandSAC)}} will be submitted to ECCV 2022 }
      \resumeItem{{Write a paper named} \textbf{\textit{Self-supervised Image Parsing}} which implements a version of the \href{https://arxiv.org/pdf/2102.12627.pdf}{\color{blue}{\textbf{\underline{GLOM}}}} model originally proposed by Geoffrey Hinton}
      \resumeItem{Open sourced the \href{https://github.com/PatrickHua/SimpleMAE}{\color{blue}{\textbf{\underline{code}}}} for self-supervised Masked Autoencoders on GitHub}
    \resumeItemListEnd

    \resumeSubheading
      {Research Assistant; Advisor: Prof. Hang Zhao}{Jan. 2021 -- Jun. 2021}
      {Tsinghua University, IIIS Multimodal Group}{Shanghai, China}
      \resumeItemListStart
        \resumeItem{\href{https://arxiv.org/pdf/2105.00470.pdf}{\color{blue}{\textbf{\underline{Paper}}}} \textbf{\textit{On Feature Decorrelation in Self-Supervised Learning}} was accepted to ICCV2021 as an \textbf{oral} presentation}
        \resumeItem{Designed experiments that reveals the connection between model collapse and feature correlations}
        \resumeItem{Open sourced the \href{https://github.com/PatrickHua/SimSiam}{\color{blue}{\textbf{\underline{code}}}} for self-supervised models Simsiam/BYOL/SimCLR/SwAV on GitHub}
      \resumeItemListEnd

    \resumeSubheading
      {Research Intern; Advisor: Dr. Yalong Bai}{Jan. 2020 -- Aug. 2020}
      {JD AI Research, CV Lab}{Beijing, China}
      \resumeItemListStart
        \resumeItem{Research \href{https://www.aaai.org/AAAI21Papers/AAAI-1020.HuaT.pdf}{\color{blue}{\textbf{\underline{paper}}}} \textit{\textbf{Relationship Matters for Multi-objects Image Generation}} accepted by AAAI 2021}
        \resumeItem{First Place in AliProducts Challenge: Large-scale Product Recognition at CVPR 2020}
        \resumeItem{Third Place in the iMet Collection Recognition Challenge at CVPR 2020 FGVC workshop}
        \resumeItem{Designed a novel mutual information adversarial training technique that will automatically
        segment objects in images}
        \resumeItem{Submitted the paper Unsupervised Image Segmentation with Contrastive Instance Distancing as
        the first author to CVPR2021}
    \resumeItemListEnd

    \resumeSubheading
      {Research Assistant; Advisor: Prof. Maithilee Kunda}{Jul. 2019 -- Sept. 2019}
      {Artificial Intelligence and Visual Analogical Systems Lab, Vanderbilt University}{Nashville, TN}
      \resumeItemListStart
        \resumeItem{Proposed a framework that leveraged an inpainting algorithm trained on photorealistic object
        images from ImageNet and achieved a score of 27/36 on the Raven’s Colored Progressive Matrices
        test which corresponds to the average performance of a nine-year-old child}
        \resumeItem{Finished the \href{https://par.nsf.gov/servlets/purl/10209969}{\color{blue}{\textbf{\underline{paper}}}} \textit{\textbf{Modeling Gestalt Visual Reasoning on Raven’s Progressive Matrices Using Generative Image Inpainting Techniques}} as the first author to target CogSci
        conference (Welcome to our Poster booth 3422 at the CogSci 2020 Virtual Conference this summer)}
      \resumeItemListEnd
      
      \resumeSubheading
      {Research Intern; Advisor: Prof. Ran He}{Aug. 2017 -- Jul. 2018}
      {Institute of Automation, Chinese Academy of Sciences (CASIA)}{Beijing, China}
      \resumeItemListStart
        \resumeItem{Reproduced the experimental results of a paper on face completion with Generative Adversarial
        Networks (GAN)}
        \resumeItem{Tested whether unpaired geometry-face datasets would lead to good quality synthesized face
        images by applying cycle-GAN structure into geometry-guided face generation}
        \resumeItem{Designed and implemented a network structure through the improvement of the DR-GAN to
        reduce the discrepancy between frontal and side face images, which contributed to an increase in
        accuracy of 5\% with the Multi-Pie dataset}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Swift, C/C++, Java, JavaScript, HTML/CSS, Bash, MATLAB} \\
     \textbf{Frameworks}{: PyTorch, JAX, TensorFlow, Flutter, Flask} \\
     \textbf{Developer Tools}{: Git, Docker, Google Cloud Platform, Amazon Web Services, VS Code, PyCharm} \\
     \textbf{Libraries}{: pandas, NumPy, SciPy, Matplotlib}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
      
